On the performance of the MAC model

### 2018-10-31 2018_nips_vigil/smac.tex
Polishing of table with parameters

\begin{table}[]
	\caption{Percentage decrease of the number of parameters by units in the MAC Cell between MAC and Simplified-MAC models}
	\centering
	\begin{tabular}{ccccCcCc}
		\toprule
	             & Read Unit               & Write Unit &  Control Unit         \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		MAC number of parameters  &  787,969 &  524,800        &    6,822,913    \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8}
	    Simplified-MAC number of parameters  & 263,168  & 262,656       &    6,560,768 \\
	    \cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8}
	     \% parameters reduction  & -67\%  &   -50\%       &      -4\%  \\
		\bottomrule
	\end{tabular}
\end{table}

>>>>

\begin{table}[]
	\caption{Numbers of trainable parameters in the units of MAC and simplified MAC cells}
	\centering
	\begin{tabular}{ccccCcCc}
		\toprule
	     Model        & Read Unit               & Write Unit &  Control Unit         \\
		\midrule
		MAC   &  787,969 &  524,800        &    6,822,913    \\
		%\midrule
	    simplified MAC & 263,168  & 262,656       &    6,560,768 \\
	    \midrule
	     Reduction [\%]  & -67\%  &   -50\%       &      -4\%  \\
		\bottomrule
	\end{tabular}
\end{table}
